---
title: "ETFproject"
output: html_document
---

rm(list = ls())

https://docs.docker.com/docker-for-mac/install/#download-docker-for-mac

"docker run -d -p 4445:4444 selenium/standalone-firefox:2.53.0"

http://localhost/

"ps docker"

despues de instalar y correr docker, lo unico que tenemos que hacer es paginar
las 20 paginas system("docker run -d -p 4445:4444
selenium/standalone-firefox:2.53.0")

#https://cran.r-project.org/web/packages/RSelenium/vignettes/RSelenium-basics.html

```{r  scrapping, echo=FALSE}

library('RSelenium')
library('XML')


#remDr <- remoteDr(browserName = "firefox", port = 4445L)


df <- data.frame(Date=as.Date(character()),
		File=character(), 
		User=character(), 
		stringsAsFactors=FALSE) 





baseURL = 'http://etfdb.com/type/sector/all/#etfs&sort_name=assets_under_management&sort_order=desc&page='

for (i in 1:3) {
	remDr <- remoteDriver(browserName = "firefox",port = 4445L)
	remDr$open()
	
	url = paste0(baseURL,i)
	remDr$navigate(url)
	remDr$refresh()

 html <- unlist(remDr$getPageSource())
 table <- readHTMLTable(html)[[2]]
 
 write.table(table, file = paste0(i , ".csv") )
 
 df <-rbind( df ,table )

 print(unlist(remDr$getCurrentUrl()))

 remDr$close()
}



 saveRDS(df, file.path(getwd(), "df.rds"))
 
 

```

at this point better if we stop Stop / remove all Docker containers to free up some resources in our system. 

docker stop $(docker ps -a -q) 
docker rm $(docker ps -a -q)



```{r  data_munging, echo=FALSE}
rm(list = ls())

library(data.table)
library(bit64)
library(dplyr)
options(digits=2)

#train <- readRDS("D:/repos/Scraping/df.rds") %>% as.data.frame() # SILENCE
setwd('/Users/davidmonteagudo/git/Scraping/')
train <- readRDS("df.rds") %>% as.data.frame() # SILENCE
class(train)


names(train) <- gsub("[\n]| ",'',names(train))   ## nicer names 
test <- train %>%    select(1,2,13)


summary(test)
str(test)


test[, c(1,2)] <- sapply(test[, c(1,2)], as.character)
test[, c(3)]<- as.numeric(sub("%", "", test[, c(3)]))

test[,order(3)]

percent_vec = paste(1:100, "%", sep = "")
as.numeric(sub("%", "", percent_vec))


library(plyr)
arrange(test,desc(3),1)

train[, c(3)] <- sapply(gsub("[$]", "", train[,3]), as.numeric)
     


median(train[,3])

train[, c(3)] <-as.numeric(sub('\\$','',as.character(train[, c(3)]))) 


class(train)


describe(train)


```

#la idea - book

 
```{r  ExploratoryAnalysis, echo=FALSE}
rm(list = ls())
 train <- readRDS("df.rds")
 

```
 
 